A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-15 paper/ms.tex
posterior table: looks decent
update ms

\begin{abstract}
  The Gaia satellite is revitalizing our understanding of nearby
  open clusters and moving groups.  Here, we focus on the
  underappreciated \cn.  Based on rotation periods from TESS and
  lithium measurements from ground-based spectrographs, we find the
  age of the cluster to be $30\pm XX$\,Myr.  \sn\ is a binary system
  in the cluster, serendipitously observed by the Kepler satellite
  because the primary is nearby and Sun-like.  Kepler\,1627A was
  previously found to host a $3.7\pm X.X\,R_\oplus$ mini-Neptune on a
  7.2\,day orbit.  We re-validate the existence of \pn, and cement it
  as the youngest planet with a well-measured age observed by the main
  Kepler mission.  Newly derived ages from Gaia offer the opportunity
  to significantly expand the census of age-dated planets -- we offer
  a literature compilation of young stars to enable this expansion.
  The properties of \pn\ are may also help clarify how the orbits and
  atmospheres of the mini-Neptune planets evolve.
\end{abstract}

@@

@@

% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}
% \input{ic2602_ages.tex}
% \input{starparams.tex}
% \input{compparams.tex}
% \input{model_posterior_table.tex}

>>>>

\begin{abstract}
  The Gaia satellite is revitalizing our understanding of nearby
  open clusters and moving groups.  Here, we focus on the
  underappreciated \cn.  Based on rotation periods from TESS and
  lithium measurements from ground-based spectrographs, we find the
  age of the cluster to be $30\pm XX$\,Myr.  \sn\ is a binary system
  in the cluster, serendipitously observed by the Kepler satellite
  because the primary is nearby and Sun-like.  Kepler\,1627A was
  previously found to host a $3.56\pm 0.04\,R_\oplus$ mini-Neptune on a
  7.2\,day orbit.  We re-validate the existence of \pn, cementing it
  as the youngest planet with a well-measured age observed by the main
  Kepler mission.  Newly derived ages from Gaia offer the opportunity
  to significantly expand the census of age-dated planets -- we offer
  a literature compilation of young stars to enable this expansion.
  The properties of \pn\ are may also help clarify how the orbits and
  atmospheres of the mini-Neptune planets evolve.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
    variability removed.}  
    The 1-$\sigma$ model uncertainties (faint purple band) and the
    median model are shown.
		\label{fig:phasefold}
	}
\end{figure*}

@@

% \input{TOI837_phot_table.tex}
% \input{TOI837_rv_table.tex}
% \input{ic2602_ages.tex}
% \input{starparams.tex}
% \input{compparams.tex}

\input{model_posterior_table.tex}
